Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-04-10 journal-draft/ettdoc.tex
add one reference

\def\volumeyear{2012}

@@

\definecolor{slightgray}{gray}{.90} 
\usepackage{rotating}
\usepackage{hhline}
\usepackage{float}
\usepackage{caption}% http://ctan.org/pkg/caption
\captionsetup[table]{format=plain,labelformat=simple,labelsep=period}%

@@

\runningheads{A.~N.~Other}{A demonstration of the \journalabb\
class file}

@@

\title{Robust Clustering for Ad Hoc Cognitive Radio Network}

\author{Di Li, Erwin Fang, James Gross\corrauth}

\address{RWTH Aachen University, ETH Zurich, KTH Royal Institute of Technology }

\corraddr{Communication Theory Lab
School of Electrical Engineering
KTH Royal Institute of Technology
SE - 100 44 Stockholm\\Email: james.gross@ee.kth.se}

@@

\section{Introduction}
\label{intro}
%CR concept
Cognitive radio (CR) is a promising technology to solve the spectrum scarcity problem~\cite{Mitola}.
Licensed users access the spectrum allocated to them whenever there is information to be transmitted.
In contrast, as one way, unlicensed users can access the spectrum via opportunistic spectrum access, \ie they access the licensed spectrum only after validating the channel is unoccupied by licensed users, where spectrum sensing~\cite{sensing_survey_2009} plays an important role in this process.
%
In this hierarchical spectrum access model~\cite{zhao_survey_DSA_2007}, the licensed users are also called primary users (PU), while the unlicensed users are referred to as secondary users and constitute a so called cognitive radio network (CRN).
%
%cluster
Regarding the operation of CRN, efficient spectrum sensing is identified to be critical for a smooth operation of a cognitive radio network~\cite{Sahai_FundamentalDesignTradeoffs2006}.
Efficient spectrum sensing can be achieved by cooperative spectrum sensing of multiple secondary users, which has been shown to cope effectively with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
Collaborative sensing relies on the consensus of CR users\footnote{The terms user and node appear interchangeably in this paper. In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer node typicallly in the context of the topology.} within a certain area, in this regard, clustering is regarded as an effective method to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing}.
% ... decreases considerably the negative probability due to the random channel effects like fading and shadowing.
Clustering is a process of grouping certain users in geographic proximity into a collective.
In the context of cognitive radio netowrks, a formed cluster helps the participants not only improve the spectrum sensing accuracy, but also coordinate the channel switch operation when the primary users are detected by at least one secondary user in that cluster, then all the cluster menmbers can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
Clustering also benefits the operation of a CRN by reducing the interference between cognitive clusters~\cite{centralizedSharing80222}, and supporting routing~\cite{Abbasi_survey_07}.
%As to the coexistence of CR users, they can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}. 
Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects, which has already been discussed in many works.

>>>>

\def\volumeyear{2017}

@@

\definecolor{slightgray}{gray}{.90} 
\usepackage{rotating}
\usepackage{hhline}
\usepackage{float}
\usepackage{caption}% http://ctan.org/pkg/caption
\captionsetup[table]{format=plain,labelformat=simple,labelsep=period}%
%\usepackage{authblk}

@@

%\runningheads{A.~N.~Other}{A demonstration of the \journalabb\
%class file}

@@

\title{Robust Clustering for Ad Hoc Cognitive Radio Network}
%\author[1]{Di Li\thanks{li@umic.rwth-aachen.de}}
%\author[2]{Erwin Fang\thanks{xx}}
%\author[3]{James Gross}
\author{Di Li, Erwin Fang, James Gross\corrauth}
%\affil[1]{RWTH Aachen University}
%\affil[2]{ETH Zurich}
%\affil[3]{KTH Royal Institute of Technology}
\address{RWTH Aachen University, ETH Zurich, KTH Royal Institute of Technology }
%\renewcommand\Authands{ and }
\corraddr{Communication Theory Lab
School of Electrical Engineering, 
KTH Royal Institute of Technology
SE - 100 44 Stockholm\\Email: james.gross@ee.kth.se}

@@

\section{Introduction}
\label{intro}
%CR concept
Cognitive radio (CR) is a promising technology to solve the spectrum scarcity problem for the upcomging era of internet of things~\cite{Mitola, Rawat20161}.
Licensed users access the spectrum allocated to them whenever there is information to be transmitted.
In contrast, as one way, unlicensed users can access the spectrum via opportunistic spectrum access, \ie they access the licensed spectrum only after validating the channel is unoccupied by licensed users, where spectrum sensing~\cite{sensing_survey_2009} plays an important role in this process.
%
In this hierarchical spectrum access model~\cite{zhao_survey_DSA_2007}, the licensed users are also called primary users (PU), while the unlicensed users are referred to as secondary users and constitute a so called cognitive radio network (CRN).
%
%cluster
Regarding the operation of CRN, efficient spectrum sensing is identified to be critical for a smooth operation of a cognitive radio network~\cite{Sahai_FundamentalDesignTradeoffs2006}.
Efficient spectrum sensing can be achieved by cooperative spectrum sensing of multiple secondary users, which has been shown to cope effectively with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
Collaborative sensing relies on the consensus of CR users\footnote{The terms user and node appear interchangeably in this paper. In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer node typicallly in the context of the topology.} within a certain area, in this regard, clustering is regarded as an effective method to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing}.
% ... decreases considerably the negative probability due to the random channel effects like fading and shadowing.
Clustering is a process of grouping certain users in geographic proximity into a collective.
In the context of cognitive radio netowrks, a formed cluster helps the participants not only improve the spectrum sensing accuracy, but also coordinate the channel switch operation when the primary users are detected by at least one secondary user in that cluster, then all the cluster menmbers can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
Clustering also benefits the operation of a CRN by reducing the interference between cognitive clusters~\cite{centralizedSharing80222}, and supporting routing~\cite{Abbasi_survey_07}.
%As to the coexistence of CR users, they can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}. 
Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects, which has already been discussed in many works.
